---
title: "Chicago Commercial Land Revised"
author: "Jack Honig"
date: "2025-02-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Introduction stuff: Getting to City-Owned commercial Properties in the 6 primary
community areas: West Englewood, Englewood, New City, North Lawndale, and the
Garfield Parks.

```{r}
setwd("/Users/jackhonig/Downloads")
CityLand <- read_csv("assessment_and_city_owned_new_data.csv")

CityLand_Com <- filter(CityLand, `Zoning Classification` != "RS-1")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RS-2")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RS-3")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RT-3.5")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RT-4")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RT-4A")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RM-4.5")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RM-5")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RM-5.5")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RM-6")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "RM-6.5")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "T")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "POS-1")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "POS-2")
CityLand_Com <- filter(CityLand_Com, `Zoning Classification` != "POS-3")
CityLand_Com <- filter(CityLand_Com, !is.na(`Zoning Classification`))


Subset_CityLand_Com <- filter(CityLand_Com, `Community Area Name` == "ENGLEWOOD"
                              | `Community Area Name` == "WEST ENGLEWOOD" | 
                              `Community Area Name` == "NEW CITY" |
                                `Community Area Name` == "NORTH LAWNDALE" | 
                                `Community Area Name` == "EAST GARFIELD PARK" | 
                                `Community Area Name` == "WEST GARFIELD PARK")
```
Now, making sure these properties are owned by the city

```{r}

Subset_cityland_owned <- filter(Subset_CityLand_Com, `Property Status` == 
                                  "Owned by City")
```

Now, dividing this by the various community areas

```{r}
#Englewood
englewood <- filter(Subset_cityland_owned, `Community Area Name` == "ENGLEWOOD")

#West Englewood
west_englewood <- filter(Subset_cityland_owned, `Community Area Name` == "WEST ENGLEWOOD")

#New City
new_city <- filter(Subset_cityland_owned, `Community Area Name` == "NEW CITY")

#East Garfield Park
east_garfield <- filter(Subset_cityland_owned, `Community Area Name` == "EAST GARFIELD PARK")

#West Garfield Park
west_garfield <- filter(Subset_cityland_owned, `Community Area Name` == "WEST GARFIELD PARK")

#North Lawndale
north_lawndale <- filter(Subset_cityland_owned, `Community Area Name` == "NORTH LAWNDALE")
```

Now, getting the number of commercial properties in each community area.

```{r}
#Englewood
nrow(englewood)

#West Englewood
nrow(west_englewood)

#New City
nrow(new_city)

#East Garfield Park
nrow(east_garfield)

#West Garfield Park
nrow(west_garfield)

#North Lawndale
nrow(north_lawndale)
```

Now, the number of square footage results for each community area

```{r}
#Englewood
englewood_sqft <- filter(englewood, `Sq. Ft.` != 0)
englewood_sqft <- filter(englewood_sqft, !is.na(`Sq. Ft.`))
nrow(englewood_sqft)

#West Englewood
west_englewood_sqft <- filter(west_englewood, `Sq. Ft.` != 0)
west_englewood_sqft <- filter(west_englewood_sqft, !is.na(`Sq. Ft.`))
nrow(west_englewood_sqft)

#New City
new_city_sqft <- filter(new_city, `Sq. Ft.` != 0)
new_city_sqft <- filter(new_city_sqft, !is.na(`Sq. Ft.`))
nrow(new_city_sqft)

#East Garfield Park
east_garfield_sqft <- filter(east_garfield, `Sq. Ft.` != 0)
east_garfield_sqft <- filter(east_garfield_sqft, !is.na(`Sq. Ft.`))
nrow(east_garfield_sqft)

#West Garfield Park
west_garfield_sqft <- filter(west_garfield, `Sq. Ft.` != 0)
west_garfield_sqft <- filter(west_garfield_sqft, !is.na(`Sq. Ft.`))
nrow(west_garfield_sqft)

#North Lawndale
north_lawndale_sqft <- filter(north_lawndale, `Sq. Ft.` != 0)
north_lawndale_sqft <- filter(north_lawndale_sqft, !is.na(`Sq. Ft.`))
nrow(north_lawndale_sqft)
```

Not a lot of results, so can't really break down these by community area. 
Instead for square footage, the median will be from all of these areas combined.

```{r}
Subset_cityland_owned_sqft <- filter(Subset_cityland_owned, `Sq. Ft.` != 0)
Subset_cityland_owned_sqft <- filter(Subset_cityland_owned_sqft, !is.na(`Sq. Ft.`))
median(Subset_cityland_owned_sqft$`Sq. Ft.`)
```

Now, we will do it with land value

```{r}
#Englewood
englewood_land <- filter(englewood, `Land Value (2022)` != 0)
englewood_land <- filter(englewood_land, !is.na(`Land Value (2022)`))
nrow(englewood_land)

#West Englewood
west_englewood_land <- filter(west_englewood, `Land Value (2022)` != 0)
west_englewood_land <- filter(west_englewood_land, !is.na(`Land Value (2022)`))
nrow(west_englewood_land)

#New City
new_city_land <- filter(new_city, `Land Value (2022)` != 0)
new_city_land <- filter(new_city_land, !is.na(`Land Value (2022)`))
nrow(new_city_land)

#East Garfield Park
east_garfield_land <- filter(east_garfield, `Land Value (2022)` != 0)
east_garfield_land <- filter(east_garfield_land, !is.na(`Land Value (2022)`))
nrow(east_garfield_land)

#West Garfield Park
west_garfield_land <- filter(west_garfield, `Land Value (2022)` != 0)
west_garfield_land <- filter(west_garfield_land, !is.na(`Land Value (2022)`))
nrow(west_garfield_land)

#North Lawndale
north_lawndale_land <- filter(north_lawndale, `Land Value (2022)` != 0)
north_lawndale_land <- filter(north_lawndale_land, !is.na(`Land Value (2022)`))
nrow(north_lawndale_land)
```
Here, there is enough data to break it out by community area, and the medians
land values can be calculated

```{r}
median(englewood_land$`Land Value (2022)`)
median(west_englewood_land$`Land Value (2022)`)
median(new_city_land$`Land Value (2022)`)
median(east_garfield_land$`Land Value (2022)`)
median(west_englewood_land$`Land Value (2022)`)
median(north_lawndale_land$`Land Value (2022)`)

Subset_cityland_owned_land <- filter(Subset_cityland_owned, `Land Value (2022)` != 0)
Subset_cityland_owned_land <- filter(Subset_cityland_owned_land, !is.na(`Land Value (2022)`))
median(Subset_cityland_owned_land$`Land Value (2022)`)
```
Now, calculating the number within TIFS, OZs, and EZs in each neighborhood

```{r}
#Englewood
englewood_TIF <- filter(englewood, !is.na(`tax_tif_district_num`))
englewood_OZ <- filter(englewood, !is.na(`econ_qualified_opportunity_zone_num`))
englewood_EZ <- filter(englewood, !is.na(`econ_enterprise_zone_num`))
nrow(englewood_TIF)
nrow(englewood_OZ)
nrow(englewood_EZ)

#West Englewood
west_englewood_TIF <- filter(west_englewood, !is.na(`tax_tif_district_num`))
west_englewood_OZ <- filter(west_englewood, !is.na(`econ_qualified_opportunity_zone_num`))
west_englewood_EZ <- filter(west_englewood, !is.na(`econ_enterprise_zone_num`))
nrow(west_englewood_TIF)
nrow(west_englewood_OZ)
nrow(west_englewood_EZ)

#New City
new_city_TIF <- filter(new_city, !is.na(`tax_tif_district_num`))
new_city_OZ <- filter(new_city, !is.na(`econ_qualified_opportunity_zone_num`))
new_city_EZ <- filter(new_city, !is.na(`econ_enterprise_zone_num`))
nrow(new_city_TIF)
nrow(new_city_OZ)
nrow(new_city_EZ)

#East Garfield Park
east_garfield_TIF <- filter(east_garfield, !is.na(`tax_tif_district_num`))
east_garfield_OZ <- filter(east_garfield, !is.na(`econ_qualified_opportunity_zone_num`))
east_garfield_EZ <- filter(east_garfield, !is.na(`econ_enterprise_zone_num`))
nrow(east_garfield_TIF)
nrow(east_garfield_OZ)
nrow(east_garfield_EZ)

#West Garfield Park
west_garfield_TIF <- filter(west_garfield, !is.na(`tax_tif_district_num`))
west_garfield_OZ <- filter(west_garfield, !is.na(`econ_qualified_opportunity_zone_num`))
west_garfield_EZ <- filter(west_garfield, !is.na(`econ_enterprise_zone_num`))
nrow(west_garfield_TIF)
nrow(west_garfield_OZ)
nrow(west_garfield_EZ)

#North Lawndale
north_lawndale_TIF <- filter(north_lawndale, !is.na(`tax_tif_district_num`))
north_lawndale_OZ <- filter(north_lawndale, !is.na(`econ_qualified_opportunity_zone_num`))
north_lawndale_EZ <- filter(north_lawndale, !is.na(`econ_enterprise_zone_num`))
nrow(north_lawndale_TIF)
nrow(north_lawndale_OZ)
nrow(north_lawndale_EZ)
```

This next part is to get the Zoning for each neighborhood.

First up: Englewood

```{r}
All_eng <- filter(CityLand, `Community Area Name` == "ENGLEWOOD")
All_eng <- filter(All_eng, `Property Status` == 
                                  "Owned by City")

Res_eng <- filter(All_eng, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_eng <- filter(Res_eng, !is.na(`Zoning Classification`))

PU_eng <- filter(All_eng, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_eng <- filter(PU_eng, !is.na(`Zoning Classification`))

```

Next, West Englewood

```{r}
All_weng <- filter(CityLand, `Community Area Name` == "WEST ENGLEWOOD")
All_weng <- filter(All_weng, `Property Status` == 
                                  "Owned by City")

Res_weng <- filter(All_weng, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_weng <- filter(Res_weng, !is.na(`Zoning Classification`))

PU_weng <- filter(All_weng, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_weng <- filter(PU_weng, !is.na(`Zoning Classification`))
```

Next, New City:

```{r}
All_ncity <- filter(CityLand, `Community Area Name` == "NEW CITY")
All_ncity <- filter(All_ncity, `Property Status` == 
                                  "Owned by City")

Res_ncity <- filter(All_ncity, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_ncity <- filter(Res_ncity, !is.na(`Zoning Classification`))

PU_ncity <- filter(All_ncity, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_ncity <- filter(PU_ncity, !is.na(`Zoning Classification`))
```

Next, East Garfield Park

```{r}
All_egar <- filter(CityLand, `Community Area Name` == "EAST GARFIELD PARK")
All_egar <- filter(All_egar, `Property Status` == 
                                  "Owned by City")

Res_egar <- filter(All_egar, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_egar <- filter(Res_egar, !is.na(`Zoning Classification`))

PU_egar <- filter(All_egar, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_egar <- filter(PU_egar, !is.na(`Zoning Classification`))
```

Next, West Garfield Park

```{r}
All_wgar <- filter(CityLand, `Community Area Name` == "WEST GARFIELD PARK")
All_wgar <- filter(All_wgar, `Property Status` == 
                                  "Owned by City")

Res_wgar <- filter(All_wgar, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_wgar <- filter(Res_wgar, !is.na(`Zoning Classification`))

PU_wgar <- filter(All_egar, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_wgar <- filter(PU_wgar, !is.na(`Zoning Classification`))
```

And Lastly, North Lawndale

```{r}
All_nlaw <- filter(CityLand, `Community Area Name` == "NORTH LAWNDALE")
All_nlaw <- filter(All_nlaw, `Property Status` == 
                                  "Owned by City")

Res_nlaw <- filter(All_nlaw, `Zoning Classification` == "RS-1" |
  `Zoning Classification` == "RS-2" | 
  `Zoning Classification` == "RS-3" |
  `Zoning Classification` == "RT-3.5" |
  `Zoning Classification` == "RT-4" |
  `Zoning Classification` == "RT-4A" |
  `Zoning Classification` == "RM-4.5" |
  `Zoning Classification` == "RM-5" |
  `Zoning Classification` == "RM-5.5" |
  `Zoning Classification` == "RM-6" |
  `Zoning Classification` == "RM-6.5")
Res_nlaw <- filter(Res_nlaw, !is.na(`Zoning Classification`))

PU_nlaw <- filter(All_nlaw, `Zoning Classification` == "T" |
  `Zoning Classification` == "POS-1" |
  `Zoning Classification` == "POS-2" |
  `Zoning Classification` == "POS-3")
PU_nlaw <- filter(PU_nlaw, !is.na(`Zoning Classification`))
```

